Haskell in Computational Biology

### 2013-05-06 jfp.tex
note on where to link figure on search

In Hughes's \citeyearpar{hughes:why} classic model of lazy search,
we~might expect to use an infinite sequence of points obtained by
applying \texttt{nextPt} to many points in succession, as done by
the Prelude function \texttt{iterate}.
But~if you look carefully at how \texttt{successors} is computed,
that's not what's happening:
instead, we~compute an infinite list by applying \texttt{nextPt} to
a~\emph{single} initial point using infinitely many distinct sources
of random variation.
Then, when we find a useful \texttt{newPt}, a~recursive call
to \texttt{everyPt} computes a \emph{fresh} infinite sequence of
single jumps starting at~\texttt{newPt}.
\mrfy's search may explore an arbitrary number of infinite
lists of points, and the representation we~found easiest to think
about is the pair of elements
\texttt{pt0}~and~\texttt{nextPt} in the \texttt{SearchGen} record.

>>>>

In Hughes's \citeyearpar{hughes:why} classic model of lazy search,
we~might expect to use an infinite sequence of points obtained by
applying \texttt{nextPt} to many points in succession, as done by
the Prelude function \texttt{iterate}.
But~if you look carefully at how \texttt{successors} is computed,
that's not what's happening:
instead, we~compute an infinite list by applying \texttt{nextPt} to
a~\emph{single} initial point using infinitely many distinct sources
of random variation.
\remark{This is the place to bring in a figure, I~think. ---NR}
Then, when we find a useful \texttt{newPt}, a~recursive call
to \texttt{everyPt} computes a \emph{fresh} infinite sequence of
single jumps starting at~\texttt{newPt}.
\mrfy's search may explore an arbitrary number of infinite
lists of points, and the representation we~found easiest to think
about is the pair of elements
\texttt{pt0}~and~\texttt{nextPt} in the \texttt{SearchGen} record.
